\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{eurosym}

% 1st arg: Author. 2nd arg: Label
\newcommand{\cit}[2]{#1 \textit{et al.} \cite{#2}}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[citecolor=black,pagebackref=true,breaklinks=true,letterpaper=true,colorlinks=true,linkcolor=black,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{Face2Face: an innovative way to face recognition \\ DL-IC 2018 Project} 

\author{D'Amico Edoardo\\
Politecnico di Milano\\
{\tt\small edoardo.damico@polimi.it}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Gabbolini Giovanni\\
Politecnico di Milano\\
{\tt\small giovanni.gabbolini@polimi.it}
\and
Parroni Federico\\
Politecnico di Milano\\
{\tt\small federico.parroni@polimi.it}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
In this paper we present a method to compare two images and get a similarity measure of these. Common usages of such a technique are really several, first of all, authentication and face matching.
\\
This system, called Face2Face, uses a deep convolutional neural network to map a couple of images into a vector of similarity features. Then, this vector is processed by the last fully-connected layers of the network which outputs a measure in the range 0,1. Training has been done by stacking couples of images one on top of the other, exploiting large convolution filters in order to capture face similarities. This method boosts also the size of the training set: in fact, each image of the N in the training set can be coupled with all the others, so $N^2$ training samples can be obtained.
\\
The main benefit of this mechanism are essentially the almost absence of hardware needed (only a camera) and the ease of use for the actual implementation. 
On the Labeled Faces in the Wild (LFW) dataset, our system achieves an accuracy of 98%.
\end{abstract}

%%%%%%%%% BODY TEXT
%------------------------------------------------------------------------

\input{intro}

\input{relatedwork}

\input{proposedapproach}

\input{experiments}

\input{conclusion}

\section*{Acknowledgements}
Here you can thank all the people that have been helpful during the project, but are not coauthors. It is important to add this section only in the final version that you send to the professors and \textbf{NOT in the review version} in order to not compromise the double blind review process. We thank Andrea Romanoni for the insightful comments during the review of the manuscript, and all the old and new Gods who stand beside us when the deadline is dark and full of terrors. 

%-------------------------------------------------------------------------
\appendix
\section{Supplementary Material} 
Supplementary material is not counted toward your 4-6 page limit and should be submitted as a separate zip file. Your supplementary material might include:
\begin{itemize}
    \item Source code (if your project proposed an algorithm, or code that is relevant and important for your project.).
    \item Cool videos, interactive visualizations, demos, etc.
\end{itemize}

\paragraph{Examples of things to NOT put in your supplementary material}
\begin{itemize}
    \item The entire PyTorch/TensorFlow Github source code.
    \item Any code that is larger than 10 MB.
    \item Model checkpoints.
    \item A computer virus.
\end{itemize}


\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\begin{thebibliography}{9}

\bibitem{google} 
Florian Schroff, Dmitry Kalenichenko and James Philbin
\textit{FaceNet: A unified embedding for face recognition and clustering}. 

\end{thebibliography}


\end{document}
